Literature review of Formal Methods applied to Blockchain technology

### 2022-01-14 article/article.tex
finish main sections

\usepackage{listings}

@@

\author{Henoch Vitureira}
\affiliation{%
  \institution{Polytechnic Institute of Setubal}
  \streetaddress{Campus do IPS - Estefanilha, 2910-761}
  \city{Setúbal}
  \country{Portugal}}
\email{2016041081@estudantes.ips.pt}

@@

//TODO FINISH

\section{Formal Modeling Application}
Blockchain systems can be divided into five main layers~\cite{Duan2018}: Data layer, Consensus layer, Smart contract layer and Application layer. 
As seen on Figure~\ref{fig:blockchain-layers}.

@@

  \begin{lstlisting}[frame=single,label={lst:block-code},
    caption={Definition of a block's structure},captionpos=b]
    newtype blockchain struct
      prehash integer;
      hash integer;
      length integer;/*the length of blocks*/
      merkleroot integer;
      ti Time;/*Timestamp*/
      translist list;
    endnewtype;

@@

  \subsubsection{Diagrams}
  With a modelling language like SDL, we can use diagrams to define blockchain structural entities, like the core system of the consensus layer
  and blocks. Process flowcharts can model the flow of information and input validation, making a process like
  node validations of blocks and its subprocess of synchronization and voting can clearly illustrated.

\section{Consensus Rule}
Blockchain system may choose to use consensus rules taken from popular protocols such as Bitcoin,
but an alternative rule can be implemented, and also be formally modelled~\cite{Kawahara2020}.

@@

\subsection{Faulty states}
Let $\mathbb{B}$ and $\mathbb{N}$ be sets of Boolean and natural numbers, respectively. The state of the \textit{i}-th node can be defined as:
$s_i = (s_i.e,s_i.v)$, where for each transaction execution, $s_i.e \in \mathbb{B}$ is the  existence of the result,
and $s_i.v \in \mathbb{B}$ is the value of the result (correct or wrong).

@@

\begin{enumerate}
  \item[$\blacksquare$] \textit{m} is a treshold
  \item[$\blacksquare$] $b \in \mathbb{B}$
  \item[$\blacksquare$] $I : \mathbb{B} \mapsto \{0,1\}$  is the indicator function
\end{enumerate}
\  \\ %fake break line

@@

\begin{displaymath}
  T.e = H_{true} \vee H_{false},  T.v = \neg{H_{false}}
\end{displaymath}

@@

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
    template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
  \item {\verb|acmsmall|}: The default journal template style.
  \item {\verb|acmlarge|}: Used by JOCCH and TAP.
  \item {\verb|acmtog|}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
  \item {\verb|acmconf|}: The default proceedings template style.
        \item{\verb|sigchi|}: Used for SIGCHI conference articles.
        \item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
        \item{\verb|sigplan|}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
  \item {\verb|anonymous,review|}: Suitable for a ``double-blind''
        conference submission. Anonymizes the work and includes line
        numbers. Use with the \verb|\acmSubmissionID| command to print the
        submission's unique ID on each page of the work.
        \item{\verb|authorversion|}: Produces a version of the work suitable
        for posting by the author.
        \item{\verb|screen|}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[sigconf]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

  {\bfseries Your document will be returned to you for revision if
    modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
  {\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

Note that authors' addresses are mandatory for journal articles.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
  \item the ``ACM Reference Format'' text on the first page.
  \item the ``rights management'' text on the first page.
  \item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

The ACM Reference Format text is required for all articles over one
page in length, and is optional for one-page articles (abstracts).

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for for all
articles over two pages in length, and are optional for one- and
two-page articles (or abstracts).

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math & Frequency   & Comments          \\
    \midrule
    \O                  & 1 in 1,000  & For Swedish names \\
    $\pi$               & 1 in 5      & Common in math    \\
    \$                  & 4 in 5      & Used in business  \\
    $\Psi^2_1$          & 1 in 40,000 & Unexplained usage \\
    \bottomrule
  \end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command                    & A Number & Comments         \\
    \midrule
    \texttt{{\char'134}author} & 100      & Author           \\
    \texttt{{\char'134}table}  & 300      & For tables       \\
    \texttt{{\char'134}table*} & 400      & For wider tables \\
    \bottomrule
  \end{tabular}
\end{table*}

Always use midrule to separate table header rows from data rows, and
use it only for this purpose. This enables assistive technologies to
recognise table headers and support their users in navigating tables
more easily.

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader.

Figure captions are placed {\itshape below} the figure.

Every figure should also have a figure description unless it is purely
decorative. These descriptions convey what’s in the image to someone
who cannot see it. They are also used by search engine crawlers for
indexing images, and when images cannot be loaded.

A figure description must be unformatted plain text less than 2000
characters long (including spaces).  {\bfseries Figure descriptions
    should not repeat the figure caption – their purpose is to capture
    important information that is not already provided in the caption or
    the main text of the paper.} For figures that convey important and
complex new information, a short text description may not be
adequate. More complex alternative descriptions can be placed in an
appendix and referenced in a short figure description. For example,
provide a data table capturing the information in a bar chart, or a
structured list representing a graph.  For additional information
regarding how best to write figure descriptions and why doing this is
so important, please see
\url{https://www.acm.org/publications/taps/describing-figures/}.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before the command
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

Some examples.  A paginated journal article \cite{Afzaal2021}, an
enumerated journal article \cite{Murray2019}, a reference to an entire
issue \cite{Matsuo2017}, a monograph (whole book) \cite{Duan2018}, a
monograph/whole book in a series (see 2a in spec. document)
\cite{Kawahara2020}, a divisible-book such as an anthology or compilation
\cite{Liu2019} followed by the same example, however we only output
the series if the volume number is given.

@@

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

>>>>

\usepackage{listings}
\usepackage{makecell}
\usepackage{tabularx}

@@

\author{Henoch Vitureira}
\affiliation{%
  \institution{Instituto Politécnico de Setúbal}
  \streetaddress{Campus do IPS - Estefanilha, 2910-761}
  \city{Setúbal}
  \country{Portugal}}
\email{2016041081@estudantes.ips.pt}

@@

Contrasting with normal testing, formal verification is performed during the design process, it ensure the design is correct and allows the verification
of any situation, while regular testing cannot test for every possible input~\cite{Murray2019}.

This paper is organized as follows. Section \ref{formalModeling} introduces applications of formal modeling of blockchain technology.
Section \ref{consensusRule} expands on the use of formal mathematical descriptions of a blockchain's consensus rule.
Section \ref{smartContracts} explored how formal modeling can be used to verify and assure quality to smart contracts using Colored Petri Nets (CPN).
Section \ref{security} elaborates on the security requirements of a blockchain system.
Section \ref{conclusion} is a brief conclusion.

\section{Formal Modeling Application}\label{formalModeling}
Blockchain systems can be divided into five main layers~\cite{Duan2018}: Data layer, Consensus layer, Smart contract layer and Application layer. 
As seen on Figure~\ref{fig:blockchain-layers}.

@@

  \begin{lstlisting}[frame=single,label={lst:block-code},
    caption={Definition of a block's structure},captionpos=b, basicstyle=\ttfamily]
    newtype blockchain struct
      prehash integer;
      hash integer;
      length integer;/*the length of blocks*/
      merkleroot integer;
      ti Time;/*Timestamp*/
      translist list;
    endnewtype;

@@

  \subsubsection{Diagrams}
  With a modeling language like SDL, we can use diagrams to define blockchain structural entities, like the core system of the consensus layer
  and blocks. Process flowcharts can model the flow of information and input validation, making a process like
  node validations of blocks and its subprocess of synchronization and voting can clearly illustrated.

\section{Consensus Rule}\label{consensusRule}
Blockchain system may choose to use consensus rules taken from popular protocols such as Bitcoin,
but an alternative rule can be implemented, and also be formally modelled~\cite{Kawahara2020}.

@@

\subsection{Faulty States}
Let $\mathbb{B}$ and $\mathbb{N}$ be sets of Boolean and natural numbers, respectively. The state of the \textit{i}-th node can be defined as:
$s_i = (s_i.e,s_i.v)$, where for each transaction execution, $s_i.e \in \mathbb{B}$ is the  existence of the result,
and $s_i.v \in \mathbb{B}$ is the value of the result (correct or wrong).

@@

\begin{enumerate}
  \item[$\blacksquare$] \textit{m} is a threshold
  \item[$\blacksquare$] $b \in \mathbb{B}$
  \item[$\blacksquare$] $I : \mathbb{B} \mapsto \{0,1\}$  is the indicator function
\end{enumerate}
\  \\ %fake break line

@@

\begin{displaymath}
  T.e = H_{\textrm{true}} \vee H_{\textrm{false}}, \quad T.v = \neg{H_{\textrm{false}}}
\end{displaymath}
\linebreak[1]

@@

Mathematical descriptions like the ones above can also be applied to the fault tolerance of organizations participating in the blockchain in question.
With formal modeling, a consensus rule can be tested and benchmarked after giving the test case some arbitrary requirements that are in conformity with the scope.
The test results are used to judge the viability and scalability of the rule.

\section{Smart Contracts}\label{smartContracts}
Smart contracts are the backend code of decentralized applications that live in blockchains such as Ethereum. 
This code cannot be changed once it is deployed to a production Net, so quality must be assured in order to guarantee
that specifications are followed and that vulnerabilities are inexistent~\cite{Murray2019}.
With the logic and mathematical modeling of formal verification, we avoid edge test cases that involve unforeseen inputs or conditions.

A smart contract's execution after its required verifications originates a transfer on a blockchain. Ethereum is a blockchain system
that allows is to deploy decentralized applications based on smart contracts, which are written in Solidity~\cite{Murray2019}.
Solidity has a limitation that makes smart contracts have a no parameters, no return value \textit{function()} that is anonymous
and defined as the fallback function~\cite{Liu2019}. When a contract sends Ether (the Ethereum blockchain token) but does not
not call any function, the fallback function is called. If this function does not exist int he contract, the transaction is cancelled.
This limitation can be used by hackers to exploit the contract, like the DAO smart contract exploit in 2016~\cite{Liu2019}.

A formal verification method using CPN modeling is proposed in~\cite{Liu2019}. In a scenario where a crowd funding smart contract (CFD) is considered, \cite{Liu2019} proposes a two layers contract modeling, 
the CFD layer model that establishes the overall structure of the contract, and a bottom layer that contains the AddTo layer
and the WithDraw layer, which implement deposit and withdrawing functions.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{cfd-layer}
  \caption{CFD Layer, from \cite{Liu2019}}
  \Description{Ilustration of the layers that describe a blockchain system}
  \label{fig:cfd-layer}
\end{figure}

The CFD layer, shown on Figure~\ref{fig:cfd-layer}, presents the entity Account, that represents the user, Bank that represent
the contract account, and Withdraw and AddTo, that represent withdrawing and depositing operations.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{add-to-layer}
  \caption{AddTo Layer, from \cite{Liu2019}}
  \Description{Ilustration of the layers that describe a blockchain system}
  \label{fig:add-to-layer}
\end{figure}

The AddTo layer, shown on Figure~\ref{fig:add-to-layer}, models the user's depositing operations, where there are 
3 transactions and 8 entities in the model that describe the steps of a given transaction in the blockchain and it's conditions.

A similar to the on seen on Figure~\ref{fig:add-to-layer} was also presented in~\cite{Liu2019} for the WithDraw layer to describe the inherent processes
of withdraw operations and all their conditions.

Models like the proposed CPN model can be tested for resilience against malicious behavior using another model that attempts to exploit
the CFD contract. We can plan our attack model to test any operation and condition, such as balance altering, assurance of reception of funds,
etc. Smart contract's vulnerabilities can be taken advantage of by regular users executing expected operations, not only by badly intended actors 
with knowledge in computer science,~so it makes sense that scenarios of no attack can also be part of the model checking. 
CPN tools like Space State Tools can used to see the status of each step of a contract's execution during a test scenario~\cite{Liu2019},
easing the discovert of vulnerabilities.

\section{Security}\label{security}
As mentioned in section~\ref{formalModeling}, formal analysis and verification is used to assure security of a blockchain's core structures and consensus rule.
But we can cover the security-requirements for backend blockchain protocol and mechanisms to ensure the assumptions and scripting language~\cite{Matsuo2017}.

In~\cite{Matsuo2017}, the authors enumerate security requirements of a blockchain system by their layers, consisting of cryptography layer, backbone protocol, application protocol,
application logic, implementation and operation. These requirements can be seen in Table~\ref{tab:security-layers}.

  \begin{table}
    \caption{Blockchain Technology layers and security considerations}
    \label{tab:security-layers}
    \begin{tabularx}{\linewidth}{ccl}
      \toprule
      Layer&Security Consideration& Standard \\
      \toprule
      Operation & \makecell{Key Management, \\Audit, Backup} & ISO/IEC 27000 \\ 
      \midrule
      Implementation & \makecell{Program Code,\\Secure Hardware} & ISO/IEC 15408 \\ 
      \midrule
      Application Logic & \makecell{Scripting Language\\for Financial\\Transaction,\\ Contract} & \makecell{Secure coding\\guides} \\ 
      \midrule
      Application Protocol & \makecell{Privacy protection,\\Secure transaction} & ISO/IEC 29128 \\ 
      \midrule
      Backbone Protocol & \makecell{PSP, Consensus,\\Merkle Tree} & ISO/IEC 29128 \\ 
      \midrule
      Cryptography & \makecell{ECDSA, SHA-2,\\RIPEMD160} & NIST, ISO \\
      \bottomrule
  \end{tabularx}
  \end{table}

We can implement formal methods in the layers Implementation, Backbone protocol, Application protocol and Language for Smart Contract.
In the implementation layer we have both software and hardware implementation pf security mechanisms, including the cryptographic algorithm,
protocols and key management mechanisms. In the Backbone protocol and application protocol deals with cryptographic protocols.
The security of the source code of a smart contracts are also mention in~\cite{Matsuo2017}, which can be modeled and verified according to requirements,
as shown in section~\ref{smartContracts}.

@@
